### 2025-09-23 Proposals/2025-NSF-EntropicGeometry/NarrativeBody.tex
Add title and notes from last week

\begin{center}
	\textbf{Title} \\
	Christine A. Aidala, University of Michigan
\end{center}
%\vspace{-8mm}

@@

>>>>

\begin{center}
	\textbf{A generalized axiomatic basis for entropic structures in physical theories} \\
	Christine A. Aidala, University of Michigan
\end{center}
%\vspace{-8mm}

@@

Notes:

Generalized ensemble spaces + geometry defined from entropy; full set of axioms

-Develop axiomatics for the entropy such that they’re physically motivated.  Not taking starting points because they’re convenient mathematically, nor because we think one physical theory (e.g. quantum mechanics) is the foundational one.

-See if this type of framework will help constrain the problem in infinite dimensions (motivation, not goal).  Need to generalize the Poisson bracket structure in infinite dimensions—relationship between entropy and Poisson brackets used as Lie brackets.  Well-known open research problem that there’s no general theory for infinite-dimensional analysis/infinite-dimensional Lie groups.

Motivation (but not goal): Eventual framework to generalize classical and quantum information theory

1. To answer fundamental questions.

2. To do classical and quantum info in a more generalized setting

3. Give a structure for infinite-dimensional analysis that’s constrained enough that mathematicians can prove theorems that are useful for physics

Have: 1. Topological structure; 2. Convex structure; 3. Geometric structure.

Open problems: 1. Entropic open balls can generate topology? 2. Are all axioms independent?   …

To determine which fundamental structures/properties are needed for all physical theories.

Open with: One of the difficulties with mathematical physics is that physicists aren’t good at specifying the mathematical requirements such that mathematicians can work effectively on the problems.

Mention economists evidently aware of topological issues more than physicists.
